Exploring Parameter Effects in the Dendritic Phase-Field Model for Crystal Formation: Part II

### 2015-12-12 comp_model/latex/paper2.tex
done with term?

\title{Exploring Theory and Anisotropy Effects in Dendritic Phase-Field Model for Crystal Formation}
\author{Elliott Capek}

@@

The larger K is, the greater the heat evolved from the solidifying crystal. Our results for crystal growth at different latent heats, shown in Figure ($\ref{fig:latent-heat}$), agrees with Shah [5]. The general effects we observe are an increase in anisotropic effects with increase in latent heat, and a decrease in growth speed and crystal size with latent heat. These results are intuitive. The $K\dot{\phi}$ term acts to magnify the effects of crystal formation. The initial conditions are set such that the field begins colder than the liquid-solid equilibrium, so crystal formation is preferred. Solidification is the only means of introducing higher temperature to the system, since the normal heat equation only serves to spread heat out. \\

@@

If latent heat is low, then little head is added to the system via crystallization and all angles of $\nabla\phi$ can crystallize. While the $\delta(\theta)$ term does add an energy cost to certain angles, we can see from Figure ($\ref{fig:latent-heat}.a$) that minimizing potential f, which heavily favors the solid phase at low temperatures, outweighs the cost of anisotropic angles.\\

@@

Figure ($\ref{fig:latent-heat-u}$) shows the temperature field for K=2.0. From this we can see that dimensionless temperature is fairly uniform around the boundary, at a value of about -0.9. At this value f still favors solidification, but it is less energetically favorable, which can explain why crystal formation is slower. \\

@@

where $\delta_0$ is the average layer width, $\mu$ is the effect of anisotropy and $\theta_0$ is the rotation of the crystal. Anisotropy is the most obvious parameter to change in this model. As expected, changing the modes in our $\delta(\theta)$ interface width changes the behavior based on circular initial conditions. Figure ($\ref{fig:anisotropy}$) shows crystal growth behavior for different anisotropies.\\

@@

Interestingly, the effect is much less pronounced for Figure ($\ref{fig:r-delta-3}$) at $a=3$. By looking at Figure ($\ref{fig:r-delta-3}$.b) we see weaker anisotropy, or more angles in the crystal interface. This can be explained by looking at Equation ($\ref{eq:kobayoshi-delta}$). When anisotropy $a$ is low, angles near the minima are less expensive than when anisotropy is high. This means that, while the system will still tend to maximize the lowest-cost angles, those near it will be more available, and thus the final crystal will have a wider variance in angles.\\

\begin{figure}[h!]
  \centering
  \textbf{a. }\includegraphics[width=0.2\textwidth]{../radial-anisotropy-4.png}
  \hspace{1cm}\textbf{b. }\includegraphics[width=0.2\textwidth]{../anis-4.png}
  \caption{\textbf{a.} Values of $\delta(\theta)$, where $\theta$ is the angular polar coordinate of points in the XY plane. Darker values correspond to larger values of $\delta$. \textbf{b.} The resulting crystal, plotted for the following parameters: $a=4$,$dx=0.0003$, $F=1.8$ and $t=0.2$.}
  \label{fig:r-delta-4}
\end{figure}

\begin{figure}[h!]
  \centering
  \textbf{a. }\includegraphics[width=0.2\textwidth]{../radial-anisotropy-3.png}
  \hspace{1cm}\textbf{b. }\includegraphics[width=0.2\textwidth]{../anis-3.png}
  \caption{$\delta$ and $\phi$, this time for $a=3$.}
  \label{fig:r-delta-3}
\end{figure}

\begin{figure}[h!]
  \centering
  \textbf{a. }\includegraphics[width=0.2\textwidth]{../radial-anisotropy-6.png}
  \hspace{1cm}\textbf{b. }\includegraphics[width=0.2\textwidth]{../anis-6.png}
  \caption{$\delta$ and $\phi$, this time for $a=6$.}
  \label{fig:r-delta-6}
\end{figure}

\subsection{Layer Thickness}
Layer thickness has an interesting effect on the crystal growth. Increasing average layer thickness $\delta_0$ in Equation ($\ref{eq:kobayoshi-delta}$) effectively increases the magnitude of the anisotropy term in our free energy definition. We see this pattern reflected in Figure ($\ref{fig:dleta}$). The highest $\delta_0$ crystal on the right seems to have the most ``anisotropy'' - it has the most offshoots, all travelling in the same direction (a minimum-energy angle in Equation ($\ref{eq:delta-6}$)). However, ``increased anisotropy'' doesn't fully describe the weirdness that arises in the $\delta_0 = 0.11$ crystal. It isn't intuitive why holes would show up in the middle of crystals. The large non-phase regions at the edges of the main dendrites, the green regions between $\phi=0$ and $\phi=1$ can be explained by accepting that at high values of anisotropy the penalties of being at a non-phase $\phi$ value imposed by potential f are less important, since the anisotropy term is being minimized.\\

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.15\textwidth]{../d-0.008-5.png}
  \includegraphics[width=0.15\textwidth]{../d-0.09-5.png}
  \includegraphics[width=0.15\textwidth]{../d-0.1-5.png}
  \includegraphics[width=0.15\textwidth]{../d-0.11-5.png}
  \caption{Effect of boundary width on crystal formation. $\delta$ values of 0.008, 0.009, 0.1 and 0.11 from left to right.}
  \label{fig:delta}
\end{figure}

\section{Variations on Model}
\subsection*{Zhao Model}
The Zhao model, described in [2], is most notable because of its use of noise to simulate thermal fluctuations in the crystal formation. The evolution equation for $\phi$ is given by:

@@

The most important part of the Zhao model is that it introduces randomness into the deterministic model. The $f_0$ term on the right is a Gaussian-sampled zero-centered term which randomly speeds up or slows down crystal formation. The effects of this added randomness are shown in [2]. The crystals evolved with noise show more small dendrites shooting off the main ones, which makes sense. Small nucleations of new dendrites can be caused by the $f_0$ term which would otherwise never show up.\\

\subsection{LDA Model}
This is less a new model and more a limiting case of the Kobayashi model. When the discussed material is particularly inert, we can make the Local Density Approximation and discount the effects of surface tension. Thus, the only energy we need to worry about is our potential, which can be given by a simple polynomial, such as the equilibrium case $f_{eq} = (1-\phi^2)^2/4$, as given in Biben [4], which gives more on this topic. In the case of this model, already existing boundaries would solidify, but extra terms are needed to actually cause crystal formation.\\

@@

\section{Reference}
\textbf{[1]} Kobayashi, R. (1993) Modeling and Numerical Simulations of Dendritic Crystal Growth. \textit{Physica D}, 63, 410-423. http://dx.doi.org/10.1016/0167-2789(93)90120-P\\
\textbf{[2]} Zhao, Y and Hou, H (2013). Simulation of Dendritic Crystal Growth of Pure Ni using the Phase-Field Model. \textit{Rev. Adv. Mater. Sci.}, 33, 246-250\\
\textbf{[3]} Sanal, R (2014). Numerical Simulation of Dendritic crystal growth using phase field method and investigating the effects of different physical parameter on the growth of the dendrite. UBid 50094548. Arxiv: http://arxiv.org/ftp/arxiv/papers/1412/1412.3197.pdf\\
\textbf{[4]} Biben, T. (2005) Phase-Field Models for Free-Boundary Problems. \textit{European Journal of Physics}, 26, 47-55. http://dx.doi.org/10.1088/0143-0807/26/5/S06
\textbf{[5]}Shah, A \textit{et. al} (2014). Numerical Simulation of Two-Dimensional Dendritic Growth Using Phase-Field Model. \textit{World Journal of Mechanics}, 128-136. http://dx.doi.org/10.4236/wjm.2014.45015
\end{document}

>>>>

\title{Exploring Parameter Effects in the Dendritic Phase-Field Model for Crystal Formation: Part II}
\author{Elliott Capek}

@@

The larger K is, the greater the heat evolved from the solidifying crystal. Our results for crystal growth at different latent heats, shown in Figure ($\ref{fig:latent-heat}$), agree with Shah [5]. The general effects we observe are an increase in anisotropic effects with increase in latent heat, and a decrease in growth speed and crystal size with latent heat. These results are intuitive. The $K\dot{\phi}$ term acts to magnify the effects of crystal formation. The initial conditions are set such that the field begins colder than the liquid-solid equilibrium, so crystal formation is preferred. Solidification is the only means of introducing higher temperature to the system, since the normal heat equation only serves to spread heat out. \\

@@

If latent heat is low, then little head is added to the system via crystallization and all angles of $\nabla\phi$ can crystallize. While the $\delta(\theta)$ term does add an energy cost to certain angles, we can see from Figure ($\ref{fig:latent-heat}.a$) that minimizing potential f, which heavily favors the solid phase at low temperatures, outweighs the cost of certain angles.\\

@@

Figure ($\ref{fig:latent-heat}$) shows the temperature field for K=2.0. From this we can see that dimensionless temperature is fairly uniform around the boundary, at a value of about -0.9. At this value f still favors solidification, but it is less energetically favorable, which can explain why crystal formation is slower. \\

@@

where $\delta_0$ is the average layer width, $\mu$ is the strength of anisotropy and $\theta_0$ is the rotation of the crystal. Anisotropy is the most obvious parameter to change in this model. As expected, changing the modes in our $\delta(\theta)$ interface width changes the behavior based on circular initial conditions. Figure ($\ref{fig:anisotropy}$) shows crystal growth behavior for different anisotropies.\\

@@

Interestingly, the effect is much less pronounced for Figure ($\ref{fig:r-delta-3}$) at $a=3$. By looking at Figure ($\ref{fig:r-delta-3}$.b) we see weaker anisotropy, or more angles in the crystal interface. This can be explained by looking at Equation ($\ref{eq:kobayoshi-delta}$). When anisotropy $a$ is low, angles near the minima are less expensive than they would be when anisotropy is high. This means that, while the system will still tend to maximize the lowest-cost angles, those near it will be more available, and thus the final crystal will have a wider variance in angles. The cosine function for lower modes is ``broader'', so the angles immediately near the minimum angles, which are dramatically more accessible to the system than those far from minima, are cheaper and therefore more represented.\\

\begin{figure}[h!]
  \centering
  \textbf{a. }\includegraphics[width=0.25\textwidth]{../radial-anisotropy-4.png}
  \hspace{1cm}\textbf{b. }\includegraphics[width=0.25\textwidth]{../anis-4.png}
  \caption{\textbf{a.} Values of $\delta(\theta)$, where $\theta$ is the angular polar coordinate, translated from the rectangular coordinates centered in the middle, of points in the XY plane. Darker values correspond to larger values of $\delta$. \textbf{b.} The resulting crystal, plotted for the following parameters: $a=4$, $dx=0.0003$, $F=1.8$ and $t=0.2$.}
  \label{fig:r-delta-4}
\end{figure}

\begin{figure}[h!]
  \centering
  \textbf{a. }\includegraphics[width=0.25\textwidth]{../radial-anisotropy-3.png}
  \hspace{1cm}\textbf{b. }\includegraphics[width=0.25\textwidth]{../anis-3.png}
  \caption{$\delta$ and $\phi$, this time for $a=3$.}
  \label{fig:r-delta-3}
\end{figure}

\begin{figure}[h!]
  \centering
  \textbf{a. }\includegraphics[width=0.25\textwidth]{../radial-anisotropy-6.png}
  \hspace{1cm}\textbf{b. }\includegraphics[width=0.25\textwidth]{../anis-6.png}
  \caption{$\delta$ and $\phi$, this time for $a=6$.}
  \label{fig:r-delta-6}
\end{figure}

\subsection{Layer Thickness}
Layer thickness has an interesting effect on the crystal growth. Increasing average layer thickness $\delta_0$ in Equation ($\ref{eq:kobayoshi-delta}$) effectively increases the magnitude of the anisotropy term in our free energy definition. We see this pattern reflected in Figure ($\ref{fig:delta}$). The highest $\delta_0$ crystal on the right seems to have the most ``anisotropy'' - it has the most offshoots, all travelling in the same direction (a minimum-energy angle in Figure ($\ref{fig:r-delta-6}$).a). The large non-phase regions at the edges of the main dendrites, the green regions between $\phi=0$ and $\phi=1$, can be explained by accepting that at high values of anisotropy the penalties of being at a non-phase $\phi$ value imposed by potential f are less important, since the anisotropy term has a larger magnitude. However, ``increased anisotropy'' doesn't fully describe the weirdness that arises in the $\delta_0 = 0.11$ crystal. It isn't intuitive why holes would show up in the middle of crystals. This is a yet unknown mystery of the $\delta_0$ parameter.\\

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.2\textwidth]{../d-0.008-5.png}
  \includegraphics[width=0.2\textwidth]{../d-0.09-5.png}
  \includegraphics[width=0.2\textwidth]{../d-0.1-5.png}
  \includegraphics[width=0.2\textwidth]{../d-0.11-5.png}
  \caption{Effect of boundary width on crystal formation. $\delta$ values of 0.008, 0.009, 0.1 and 0.11 from left to right.}
  \label{fig:delta}
\end{figure}

\section{Variations on Model}
\subsection{Zhao Model}
The Zhao model, described in [2], is most notable because of its use of noise to simulate thermal fluctuations in the crystal formation. The evolution equation for $\phi$ is given by:

@@

The most important part of the Zhao model is that it introduces randomness into the deterministic Kobayashi model. The $f_0$ term on the right is a Gaussian-sampled zero-centered term which randomly speeds up or slows down crystal formation. The effects of this added randomness are shown in [2]. The crystals evolved with noise show more small dendrites shooting off the main ones, which makes sense. Small nucleations of new dendrites can be caused by the $f_0$ term which would otherwise never show up.\\

\subsection{LDA Model}
This is less a new model and more a limiting case of the Kobayashi model. When the discussed material is particularly inert, we can make the Local Density Approximation and discount the effects of surface tension. Thus, the only energy we need to worry about is our potential, which can be given by a simple polynomial, such as the equilibrium case $f_{eq} = (1-\phi^2)^2/4$, as given in Biben [4]. In the case of this model, already existing boundaries would solidify, but extra terms are needed to actually cause crystal formation.\\

@@

\section{Reference}
\textbf{[1]} Kobayashi, R. (1993) Modeling and Numerical Simulations of Dendritic Crystal Growth. \textit{Physica D}, 63, 410-423. http://dx.doi.org/10.1016/0167-2789(93)90120-P\\
\textbf{[2]} Zhao, Y and Hou, H (2013). Simulation of Dendritic Crystal Growth of Pure Ni using the Phase-Field Model. \textit{Rev. Adv. Mater. Sci.}, 33, 246-250\\
\textbf{[3]} Sanal, R (2014). Numerical Simulation of Dendritic crystal growth using phase field method and investigating the effects of different physical parameter on the growth of the dendrite. UBid 50094548. Arxiv: http://arxiv.org/ftp/arxiv/papers/1412/1412.3197.pdf\\
\textbf{[4]} Biben, T. (2005) Phase-Field Models for Free-Boundary Problems. \textit{European Journal of Physics}, 26, 47-55. http://dx.doi.org/10.1088/0143-0807/26/5/S06\\
\textbf{[5]} Shah, A \textit{et. al} (2014). Numerical Simulation of Two-Dimensional Dendritic Growth Using Phase-Field Model. \textit{World Journal of Mechanics}, 128-136. http://dx.doi.org/10.4236/wjm.2014.45015
\end{document}
